Tungsten Disulfides and Tungsten Oxides Core-Shell NWs

### 2014-03-11 ch-tms/Seeded_growth_draft.tex
moox structure adjusted

$6\mu L$ Methylene Blue\footnote{\ce{C16H18N3SCl} molar mass 319.85g/mol.} (Alfa Aesar 42771, 1\%w/v = 31.26 mM) in diluted into 20 mL DI water, giving ultimate concentration as $9.38 \mu M$. The measured absorbance spectrum is shown in supporting information, with maximum absorbance 0.42 at 664nm. Taking the \ce{MB^+} molar extinction coefficient $\epsilon$ as 95000 $M^{-1}cm^{-1}$,\cite{Cenens1988} then the measured concentration is $c = \frac{A}{\epsilon l}$ is $4.37 \mu M$.

@@

\cite{Breault2013} \ce{TiO2} on MB degradation rate. aliquots, adsorption and desorption equilibrium and how to measure it. Discuss the distinguish of MB and LMB by nitrogen and oxygen purging. The author also mention the pH value change is an indictor of complete mineralization. The formatin of superoxide and hydroxyl radicals has been experimentally determined by radical quenchers.
\ce{I^-} is a scavenger for VB holes, and \ce{.OH}. Adding 2mM KI will reduce the rate.

>>>>

Photocatalytic performance of as-synthesized core-shell NWs was evaluated by measuring the degradation of MB. Xe-Hg lamp ( ) and a liquid filter were used to provide UV and visible irradiation and a glass filter was applied to cut off UV light (below 420 nm). All vessel and beaker are of borosilicate glass type (Pyrex), which was reported to adsorb little MB.\cite{Chakrabarti2005} In a typical experiment, 10 mL aqueous solution containing about 1 mg sample was mixed with 50 mL of $10 \mu M$ MB solution. The mixture was magnetically stirred in dark for 1 hr to allow for MB adsorption, during which the solution was sampled several times for UV-Vis measurement to confirm the equilibrium and to serve as reference point. Then the solution was continuously purged with oxygen or argon (20 sccm) and magnetically stirred (80 rmp) throughout the reaction process. No thermal bath was used but the solution temperature was monitored and the variation was found to be less than 3 K. Sample of the solution was withdraw regularly with respect to irradiation time, placed into a quartz cuvette and capped with plastic septum to isolate external moisture. The UV-Vis absorbance spectra were taken in a two beam configuration, with a paired quartz cuvette containing DI water as reference. The catalyst absorbance spectrum only provide a scattering background onto which the MB spectra is superimposed. Thus no centrifugation is employed since it does not interfere with evaluating absorbance of MB. The extent to which MB is photodecomposed was calculated the absorbance variation at 663nm. It has been known that MB can also be reduced to colorless lecuo form with absorption peak at 256 nm in aqueous solution.\cite{Mills1999} This might cause overestimation of the photocatalyst efficiency. To avoid this ambiguity, the possible formation of lecuo MB was probed by oxygen purging the solution in dark and measuring the UV-Vis spectrum again.

Methylene Blue\footnote{\ce{C16H18N3SCl} molar mass 319.85g/mol.} (Alfa Aesar 42771, 1\%w/v = 31.26 mM) is diluted into DI water to prepare reaction solution with concentration about $10 \mu M$. The measured absorbance spectrum is shown in supporting information, with maximum absorbance 0.42 at 664nm. Taking the \ce{MB^+} molar extinction coefficient $\epsilon$ as 95000 $M^{-1}cm^{-1}$,\cite{Cenens1988} then the measured concentration is $c = \frac{A}{\epsilon l}$ is $4.37 \mu M$.

@@

 \ce{TiO2} on MB degradation rate. aliquots, adsorption and desorption equilibrium and how to measure it. Discuss the distinguish of MB and LMB by nitrogen and oxygen purging. The author also mention the pH value change is an indictor of complete mineralization. The formatin of superoxide and hydroxyl radicals has been experimentally determined by radical quenchers.\cite{Breault2013}
\ce{I^-} is a scavenger for VB holes, and \ce{.OH}. Adding 2mM KI will reduce the rate.
